Mechanistic Bayesian Forecasts of COVID19

### 2020-07-26 paper.tex
i hate git

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{tikz}

@@

 \begin{itemize}
 \item Because of detection probability we cannot seed using initial reported data, since this is an underestimate
  \end{itemize}

>>>>

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{subcaption}

@@

 \begin{itemize}
 \item Because of detection probability we cannot seed using initial reported data, since this is an underestimate
 \item Put priors on initial seed
  \end{itemize}

  \subsection{Priors}

 \begin{itemize}
 \item We choose tight priors based on literature
  \item Fundamental unidentifiability due to renewal equation expression where $I(t)$ is a convolution between $R_t$ and Seiral interval
  \item Cannot estimate both simultaneously 
  \item Most flexibility comes in with beta and detection random walk
  \item Ideal for forecasting, maybe not for inference
  \end{itemize}

  \subsection{Fitting}

 \begin{itemize}
 \item Fully Bayesian HMC on parameters
 \item Why we choose deterministic compartmental model with only uncertainty on parameters and observations
 \item Estimation in numpyro very fast
   \end{itemize}

 \section{Experimental Setup}

 \subsection{COVID-HUB}
 \begin{itemize}
 \item Real-time forecasting evaluation for 14 weeks starting April 20th 2020. 
 \item Forecasts submitted every Monday using incident data up until Sunday
 \item Cumulative forecasts generated by aggregation of incident forecasts
 \item 1-4 week ahead targets generated from 28 day ahead predictions 
 \end{itemize}

 \subsection{Ablation Test}
 \begin{itemize}
 \item Evaluate a set of nested models
 \begin{itemize}
 \item Basic SEIR model with observations only on deaths
 \item SEIR with joint observations
 \item SEIR with joint observations and random walk detection probability
 \end{itemize}
 \item We omit the test that involves no random walk on beta since a model must take into account interventions.

\section{Results}

\begin{figure}
  \centering
     \begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.5]{US.png}
    \caption{US}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.5]{NY.png}
    \caption{New York}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.5]{FL.png}
    \caption{Florida}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
    \includegraphics[scale=.5]{CA.png}
    \caption{California}
\end{subfigure}%

\caption{Example fit and forecast for four states.}
\label{fig:fit_and_forecast_results}
\end{figure}

 \begin{figure}
     \centering
     \includegraphics[scale=.1]{beta_t_plot.png}
     \caption{Deaths by state. }
     \label{fig:my_label}
 \end{figure}
  \begin{figure}
     \centering
     \includegraphics[scale=.1]{detection_plot.png}
     \caption{Deaths by state. }
     \label{fig:my_label}
 \end{figure}

\begin{itemize}
\item MechBayes is uniformly better than baseline model when broken down by region and timezero.
\end{itemize}
